{\acronym} meets FOX: an ensemble approach to entity linking based on vector similarity

### 2015-08-20 paper.tex
- added upper bound values for precision and recall for both datasets

Table~\ref{table:redirects1} shows the evaluation results. 
\acronym{} outperforms both FOX and DBpedia Spotlight on the AIDA-YAGO dataset and achieves slightly worse but comparable results on the KORE50 dataset. 
The latter is due to the fact that KORE50 was designed to have a high degree of ambiguity and short sentences, which renders {\acronym 's} approach less effective: Short sentences provide fewer tokens to evaluate a tf-idf overlap, while increased numbers of candidates allow for more detrimental semantic neighborhood signature vector overlaps.

>>>>

The quality of the NER used to find entities poses an upper bound on the achievable entity linking scores. For the AIDA/CoNLL dataset the highest achievable linking precision is 0.79, while the highest achievable recall is 0.98 (max. $F_1$: 0.88). For the KORE50 dataset the values are 0.93 and 0.88 respectively (max. $F_1$: 0.90).

Table~\ref{table:redirects1} shows the evaluation results. 
\acronym{} outperforms both FOX and DBpedia Spotlight on the AIDA/CoNLL dataset and achieves slightly worse but comparable results on the KORE50 dataset. 
The latter is due to the fact that KORE50 was designed to have a high degree of ambiguity and short sentences, which renders {\acronym 's} approach less effective: Short sentences provide fewer tokens to evaluate a tf-idf overlap, while increased numbers of candidates allow for more detrimental semantic neighborhood signature vector overlaps.
